HTW E3 Testing

### 2023-10-09 Analysis/e3_test.qmd
automate stats fix

```{r}
#| label: fig-e3-test-vx
#| fig-cap: e3 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
#| fig-width: 11
#| fig-height: 9
# testE3 |> filter(bandOrder=="Original")|> group_by(id,vb,condit) |> plot_distByCondit()
# testE3 |> filter(bandOrder=="Reverse")|> group_by(id,vb,condit) |> plot_distByCondit() +ggtitle("test")

>>>>

```{r}
#| label: fig-e3-test-vx
#| fig-cap: e3 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
#| fig-width: 13
#| fig-height: 11
# testE3 |> filter(bandOrder=="Original")|> group_by(id,vb,condit) |> plot_distByCondit()
# testE3 |> filter(bandOrder=="Reverse")|> group_by(id,vb,condit) |> plot_distByCondit() +ggtitle("test")
